Fast solvers for partial differential equations \\ subject to inequalities

### 2023-11-09 talk-dms/slides.tex
basically the figure sequence ...

\only<1-2>{\includegraphics[width=0.4\textwidth]{../talk-oxford/images/obstacle65.pdf}}
\hfill
\only<1-2>{\includegraphics[width=0.25\textwidth]{../paper/fixfigs/ball-set.png} \hspace{1mm}}
\only<3>{\includegraphics[width=0.25\textwidth]{../paper/fixfigs/spiral-set.png} \hspace{2mm}}

\begin{itemize}
\item<1> plot $m_J$ versus V-cycle iterations for ball from Table 2 and fit $\log(m_J)$
\item<2> add $m_J$ versus F-cycle iterations for ball from Table 2
\item<3> plot $m_J$ versus V-cycle, F-cycle iterations for spiral from Table 2 and fit $\log(m_J)$
\end{itemize}
\end{frame}

>>>>

\only<1-2>{\includegraphics[width=0.4\textwidth]{../talk-oxford/images/obstacle65.pdf}}
\hfill
\only<1-2>{\includegraphics[width=0.2\textwidth]{../paper/fixfigs/ball-set.png} \hspace{1mm}}
\only<3>{\includegraphics[width=0.2\textwidth]{../paper/fixfigs/spiral-set.png} \hspace{2mm}}

\bigskip

\begin{center}
%\only<1>{\includegraphics[width=0.25\textwidth]{figs/balliterslog.png}}
\only<1>{\includegraphics[width=0.5\textwidth]{figs/balliters.png}}
\only<2>{\includegraphics[width=0.5\textwidth]{figs/balliters.png}}
\only<3>{\includegraphics[width=0.5\textwidth]{figs/bothiters.png}}
\end{center}

%\item<1> plot $m_J$ versus V-cycle iterations for ball from Table 2 and fit $\log(m_J)$
%\item<2> add $m_J$ versus F-cycle iterations for ball from Table 2
%\item<3> plot $m_J$ versus V-cycle, F-cycle iterations for spiral from Table 2 and fit $\log(m_J)$
\end{frame}
